---
title: "CptS 575_Assignment 04"
author: "Sajjad Uddin Mahmud | WSU ID: 011789534"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Setting the file location
setwd("D:/Homeworks/Data_Science/Assignment 04")
```

# Solution of Problem 01 : 

## Solution of 1(a)

```{r, warning = FALSE, message=FALSE}

# Loading the packages
library(nycflights13)
library(dplyr)

# Reading the data set

weather %>%
  select(origin,year,month,day,hour,humid) %>%
  filter(year==2013, month==11, day==1, hour>=12 & hour<=18) ->
  Weather_Data

flights %>%
  select(dest, dep_time, tailnum, year, month, day, hour, origin) %>%
  filter(dest == "TPA", year == 2013, month == 11, day == 1, dep_time >= 1200 
         & dep_time<=1800) %>%
  mutate(hour = round(dep_time/100)) %>%
  left_join(Weather_Data, by = c("origin" = "origin", "year" = "year", 
                                 "month" = "month", "day" = "day", "hour"="hour")) ->
  Flight_Data_Tampa
  
Flight_Data_Tampa 


```

There are **6** flights happened during the given time frame.

## Solution of 1(b)

```{r, warning = FALSE, message=FALSE}
Anti_Join_1 <- anti_join(flights, airports, by = c("origin" = "faa"))

Anti_Join_1

Anti_Join_2 <- anti_join(airports, flights, by = c("faa" = "origin"))

Anti_Join_2

```

**Difference between Anti_Join_1 and Anti_Join_2**

We know that anti_join() return all rows from X dataset without a match in Y dataset.

In Anti_Join_1, we are looking into rows of flights dataset that are not in the airports dataset for "origin=faa". As in the flights dataset, there are only EWR, JFK and LGA airports, hence it returns zero rows.

In Anti_Join_2, we are looking into rows of airports dataset that are not in the flights dataset for "faa=origin" condition. As a result, we can see 1455 rows. Because the total rows were 1458 and it excludes 3 (EWR, JFK and LGA) from that.  


**Difference between semi_join and anti_join**

With just the columns from X dataset kept, semi join(X,Y) returns all rows from X where there are matching values in Y. On the contrary, anti join(X,Y) only keeps the columns from X and returns all rows from X where there are no matching values in Y.  

\newpage
## Solution of 1(c)

```{r, warning = FALSE, message=FALSE}

flights %>%
  select(origin, dest) ->
  Flight_Routes

airports %>%
  select(faa,lat,lon) ->
  Airport_Locations

Flights_Data <- inner_join(Flight_Routes,Airport_Locations, by = c("dest" = "faa"))

Flights_Data
```

There are **329,174** flights.  


## Solution of 1(d)

```{r, warning = FALSE, message=FALSE}

flights %>%
  group_by(carrier, dest) %>%
  count(sort = TRUE) ->
  Flights_Summary

Flights_Summary

```

There are **314** unique combinations of carrier/dest present in the dataset.  


## Solution of 1(e)

```{r, warning = FALSE, message=FALSE}

# Loading the packages
library(maps)
library(usmap)
library(ggplot2)

# Getting the data to map
flights %>%
  select(origin) %>%
  left_join(airports, by = c("origin" = "faa")) %>%
  group_by(origin) %>%
  select(origin,lat,lon) %>%
  summarise(Total_Flight_Number = n()) ->
  Flight_Origin_Map_Data

Flight_Origin_Map_Data

Flight_Origin_Map_Data %>%
  left_join(airports, c("origin" = "faa")) ->
  Flight_Origin_Map_Data

Flight_Origin_Map_Data %>%
  ggplot(aes(lon,lat, label = origin))+
  borders("state", xlim = c(-74.5,-73.5), ylim = c(40.8,41)) +
  geom_point(aes(colour = Total_Flight_Number)) +
  labs(x="Longitude", y="Latitude", title="Outgoing Flights")



```


\newpage

# Solution of Problem 02

For this problem, I have chosen US President Election Year 2016 and 2020 for the visualization.

```{r, warning = FALSE, message=FALSE}

# Loading the packages
library(usmap)
library(ggplot2)
library(RColorBrewer)


# Reading the data set
US_President <- read.csv("us-presidents.csv")

# Creating a visualization of the total number of voter in US President Election

# Year 2016
US_President %>%
  group_by(year) %>% 
  filter(year=="2016") ->
  US_Map_Data

Plot_US_Election1 <- plot_usmap(data=US_Map_Data,values="totalvotes",
                                labels = TRUE, label_color="white")+
  scale_fill_continuous(name="Total No. of Voter",low="slateblue4",
                        high="skyblue",label=scales::comma)+
  theme(legend.position = "right") + labs(caption="Figure 01: US Election 2016")

Plot_US_Election1

# Year 2020
US_President %>%
  group_by(year) %>% 
  filter(year=="2020") ->
  US_Map_Data

Plot_US_Election2 <- plot_usmap(data=US_Map_Data,values="totalvotes",
                                labels = TRUE, label_color="white")+
  scale_fill_continuous(name="Total No. of Voter",low="mediumpurple4",
                        high="mediumorchid1",label=scales::comma)+
  theme(legend.position = "right") + labs(caption="Figure 02: US Election 2020")

Plot_US_Election2

```

  
\newpage

# Solution of Problem 03: Word Cloud

For this problem, I have chosen my "Statement of Purpose" as the input document.

```{r, warning = FALSE, message=FALSE, tidy=TRUE}

# Initialization
library(wordcloud)
library(RColorBrewer)
library(tm)
library(plotly)

# Reading the word document
Word_File_Text <- readLines("D:\\Homeworks\\Data_Science\\Assignment 04\\Statement_of_purpose_Sajjad.txt")

Word_File_Text <- Corpus(VectorSource(Word_File_Text))

# Tidying the document
Word_File_Text %>%
  tm_map(content_transformer(tolower)) %>% # Converting all words in lowercase
  tm_map(removeNumbers) %>% # Removing numbers
  tm_map(removeWords, stopwords("english")) %>% # Removing stop words
  tm_map(removeWords, c("also", "become", "sajjad", "mahmud")) %>% # Removing some specific words
  tm_map(removePunctuation) %>% # Removing punctuation
  tm_map(stripWhitespace) -> # Collapsing multiple white space characters to a single blank
  Word_File_Text 

# Creating Title
layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, 
     "Sajjad's Statement of Purpose for WSU Application, written in August 2021")

# Generating the wordcloud
wordcloud(Word_File_Text, min.freq = 1, max.words = 200, random.order=FALSE, 
          colors=brewer.pal(12,"Set1"))

```


